Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-02 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Aesthetics

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }

% Color scheme and sidebar
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
\definecolor{bluemunsell}{rgb}{0.0, 0.5, 0.69}
%#09BADB #DB1A71
\usetheme[right]{Berkeley}
\setbeamercolor{palette primary}{bg=ceruleanblue,fg=white}
\setbeamercolor{palette secondary}{bg=bleudefrance,fg=white}
%\setbeamercolor{sidebar}{bg=bleudefrance}

@@

\usefonttheme{serif}
\setbeamercovered{invisible}

\title[]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
\author[]{Julius R{\"u}schenp{\"o}hler\inst{*}}
\institute[]{\inst{*} UC Berkeley, CEGA}
\date{March 04, 2021}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize}
	\item Bloom and van Reenen (2010): Heterogeneity
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Value-Added of Business Practices}
	\begin{itemize}
	\item Bloom and van Reenen (2019): Correlation with productivity
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
	\vspace{0.2in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Best Practices for Small Firms}
	\begin{itemize}
	\item McKenzie and Woodruff (2017): Portable best practices
	\vspace{0.2in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize}
	\item At least \textcolor{bleudefrance}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
	\vspace{0.1in}
	\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
	\vspace{0.2in}
	\item Examples: Start and Improve Your Business (ILO), Business Edge (IFC), \textcolor{red}{ELSE??}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize}
	\item Content %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize}
	\item Delivery %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize}
	\item Recent evaluations (McKenzie, 2020)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize}
	\item Female entrepreneurs
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize}
	\item Young entrepreneurs
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize}
	\item Gazelles
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize}
	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize}
	\item ?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}
	\begin{itemize}
	\item Confidence Intervals, pic?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize}
	\item Self-reports of aggregate
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize}
	\item Disaggregating quantities in self-reports
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize}
	\item Direct measures
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{?}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize}
	\item Heterogeneity of treatment effect poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Education}
	\begin{itemize}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Family Commitments}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Identity Concerns}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Aspirations}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Local Relevance of Best Practices}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize}
	\item 
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
	\vspace{0.1in}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Takeaways}
	\begin{itemize}
    \item
   	\vspace{0.10in}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Questions}
	\begin{itemize}
	\item Any questions?
	\vspace{0.2in}
	\item[] .. before we move on to our paper?
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Background}
	\begin{itemize}
	\item Micro \& Small firms (MSEs) main \textbf{source of employment} in the developing world
	\vspace{0.2in}
	\item In \textbf{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
	\vspace{0.2in}
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize}
\item \textbf{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.2in}
\item \textbf{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.2in}

\item \textbf{Mobilizing Peer Knowledge}:
    \begin{itemize}
    \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
    \item Cai \& Szeidl (2018) $\rightarrow$ Business meetings
    \item Abebe et al. (2019) $\rightarrow$ Management experience matching
    \end{itemize}
    \vspace{0.2in}
\end{itemize}
\end{frame}

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
\begin{itemize}
\item Some facts about business practices in firms:
	\begin{itemize}	
	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
	\end{itemize}
\vspace{0.2in}
\pause
\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
\vspace{0.2in}
\pause
\item Our idea is to make it \textbf{central} to the research design: 
	\begin{itemize}
	\item Use variation across businesses to identify business practices associated with successful performance
	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
	\item Test different communication channels and their cost-effectiveness
\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Selecting Local Best Practices}
\begin{itemize}
\item Detailed \textcolor[rgb]{0.00,0.07,1.00}{qualitative interviews} with local business peers:
    \begin{itemize}
    \item Understand and codify their practices (record-keeping, financial planning, stocking-up, marketing, and joint decision-making)
    \item Identify implementation norms and beliefs regarding each practice (e.g. whether they are complicated, necessary, etc.)
    \item Document locally relevant tips and rule of thumbs
    \end{itemize}
\vspace{0.2in}
\item Baseline \textcolor[rgb]{0.00,0.07,1.00}{quantitative survey}
    \begin{itemize}
    \item Measure practices and outcomes
    \item Quantitative association of business practices with profits and sales
    \end{itemize}
\end{itemize}
\end{frame}

%
\begin{frame}
\frametitle{Disseminating Knowledge}
		\begin{itemize}
		\item \textbf{Handbook}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Pure information}: Which practices, how to adopt, and why?\\
            %\item \textbf{Positive Frame}: Retailers who implement [x] report y\% \textbf{higher} sales and z\% \textbf{higher} profits.
            %\item \textbf{Negative Frame}: Retailers who do \textbf{not} implement [x] report y\% \textbf{lower} sales and z\% \textbf{lower} profits.
			\end{itemize}
\bigskip
Supplemented with two types of experiential learning:
\bigskip
		\item \textbf{Movie}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textbf{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
			\end{itemize}

\bigskip
		\item \textbf{In-shop Assistance}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textbf{experience, with a small nudge} (Kolb, 1984).
			\item Facilitated by local lay person
			\end{itemize}
			\vspace{0.05in}
%\bigskip
%			$\rightarrow$ Horse race between role models and business counseling.
		\end{itemize}

@@

\begin{frame}
\frametitle{Research Questions}
	\begin{itemize}
	%\item \textbf{Local characterization}
	%\vspace{0.05in}
	%	\begin{itemize}
	%	\item Which practices are associated with high profits?
	%	\item How do successful businesses implement them?
	%	\end{itemize}
	%\vspace{0.05in}
	\item \textbf{Adoption}
		\begin{itemize}
		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
		\item If so, ...
			\begin{itemize}
			\item Does the type of experiential involvement matter?
			\end{itemize}
		\end{itemize}
    \vspace{0.3in}
	\item \textbf{Impact}
		\begin{itemize}
		\item Does firm profitability increase?
		\item If so, what are the channels?
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Retail Shop in the Sample II}

@@

\begin{frame}
\frametitle{Handbook}

@@

\begin{frame}
\frametitle{Handbook Content II}

@@

	\end{table}}}
\begin{itemize}
\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
\end{itemize}
\end{frame}

>>>>

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
\newenvironment{itemize_3pt}{\itemize\addtolength{\itemsep}{3pt}}{\enditemize}
\newenvironment{enumerate_3pt}{\enumerate\addtolength{\itemsep}{3pt}}{\endenumerate}

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}

% Color scheme
\definecolor{cerulean}{rgb}{0.16, 0.32, 0.75}
\definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
\definecolor{offwhite}{RGB}{255,253,238}
\definecolor{red}{RGB}{213,94,0}
%#09BADB #DB1A71

\usetheme[right]{Berkeley}
\setbeamercolor{background canvas}{bg=offwhite}
\setbeamercolor{palette primary}{bg=cerulean,fg=white}
\setbeamercolor{palette secondary}{bg=bdf,fg=white}
\setbeamercolor{frametitle}{fg=offwhite}
%\setbeamercolor{sidebar}{bg=cerulean}

%\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
%\setbeamercolor{title}{fg=black}
%\setbeamercolor{itemize item}{fg=blue}
%\setbeamercolor{itemize subitem}{fg=blue}
%\setbeamercolor{enumerate item}{fg=blue}
%\setbeamercolor{enumerate subitem}{fg=blue}
%\setbeamercolor{button}{bg=offwhite,fg=blue}

\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}

% Page number and navigation
\setbeamerfont{page number in head/foot}{size=\small}
%\setbeamertemplate{footline}[frame number]
\setbeamertemplate{navigation symbols}{}

\addtobeamertemplate{footline}
{%
   \usebeamercolor[fg]{author in sidebar}
   \vskip-1cm\hskip8pt
   \insertframenumber\,/\,\inserttotalframenumber\kern1em\vskip4pt%
}

@@

\title[]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
\author[]{Julius R{\"u}schenp{\"o}hler\inst{}}
\institute[]{\inst{} UC Berkeley, CEGA}
\date{March 04, 2021}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010): Heterogeneity
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2019): Correlation with productivity
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Best Practices for Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2017): Portable best practices
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

%\begin{frame}
%\begin{center}
%{ \Huge \textcolor{black}{Classical MSME Training}}
%\end{center}
%\end{frame}

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_3pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\vspace{0.1in}
		\item Examples:
		\begin{itemize_3pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_3pt} 
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize_3pt}
	\item Content %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize_3pt}
	\item Delivery %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize_3pt}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize_3pt}
	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize_3pt}
	\item Recent evaluations (McKenzie, 2020)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize_3pt}
	\item Female entrepreneurs
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize_3pt}
	\item Young entrepreneurs
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize_3pt}
	\item Gazelles
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_3pt}
	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_3pt}
	\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_3pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_3pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}
	\begin{itemize_3pt}
	\item Confidence Intervals, pic?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Self-reports of aggregate
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Disaggregating quantities in self-reports
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize_3pt}
	\item Direct measures
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize_3pt}
	\item Heterogeneity of treatment effect poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Education and literacy}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Family Commitments}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Identity Concerns}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Aspirations}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Local Relevance of Best Practices}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_3pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_3pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_3pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_3pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_3pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_3pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Takeaways}
	\begin{itemize_3pt}
    \item
   	\vspace{0.10in}
\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Questions}
	\begin{itemize_3pt}
	\item Any questions?
	\vspace{0.1in}
	\item[] .. before we move on to our paper?
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Background}
	\begin{itemize_3pt}
	\item Micro \& Small firms (MSEs) main \textcolor{bdf}{source of employment} in the developing world
	\vspace{0.1in}
	\item In \textcolor{bdf}{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
	\vspace{0.1in}
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize_3pt}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_3pt}
\item \textcolor{bdf}{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.1in}

\item \textcolor{bdf}{Mobilizing Peer Knowledge}:
    \begin{itemize_3pt}
    \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
    \item Cai \& Szeidl (2018) $\rightarrow$ Business meetings
    \item Abebe et al. (2019) $\rightarrow$ Management experience matching
    \end{itemize_3pt}
    \vspace{0.1in}
\end{itemize_3pt}
\end{frame}

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
\begin{itemize_3pt}
\item Some facts about business practices in firms:
	\begin{itemize_3pt}	
	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
	\end{itemize_3pt}
\vspace{0.1in}
\pause
\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
\vspace{0.1in}
\pause
\item Our idea is to make it \textcolor{bdf}{central} to the research design: 
	\begin{itemize_3pt}
	\item Use variation across businesses to identify business practices associated with successful performance
	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
	\item Test different communication channels and their cost-effectiveness
\end{itemize_3pt}
\end{itemize_3pt}

@@

\begin{frame}
\frametitle{Selecting Local Best Practices}
\begin{itemize_3pt}
\item Detailed \textcolor{bdf}{qualitative interviews} with local business peers:
    \begin{itemize_3pt}
    \item Understand and codify their practices (record-keeping, financial planning, stocking-up, marketing, and joint decision-making)
    \item Identify implementation norms and beliefs regarding each practice (e.g. whether they are complicated, necessary, etc.)
    \item Document locally relevant tips and rule of thumbs
    \end{itemize_3pt}
\vspace{0.1in}
\item Baseline \textcolor{bdf}{quantitative survey}
    \begin{itemize_3pt}
    \item Measure practices and outcomes
    \item Quantitative association of business practices with profits and sales
    \end{itemize_3pt}
\end{itemize_3pt}
\end{frame}

%
\begin{frame}
\frametitle{Disseminating Knowledge}
		\begin{itemize_3pt}
		\item \textcolor{bdf}{Handbook}
			\begin{itemize_3pt}
			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
            %\item \textcolor{bdf}{Positive Frame}: Retailers who implement [x] report y\% \textcolor{bdf}{higher} sales and z\% \textcolor{bdf}{higher} profits.
            %\item \textcolor{bdf}{Negative Frame}: Retailers who do \textcolor{bdf}{not} implement [x] report y\% \textcolor{bdf}{lower} sales and z\% \textcolor{bdf}{lower} profits.
			\end{itemize_3pt}
\bigskip
Supplemented with two types of experiential learning:
\bigskip
		\item \textcolor{bdf}{Movie}
			\begin{itemize_3pt}
			\item \textcolor{bdf}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textcolor{bdf}{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
			\end{itemize_3pt}

\bigskip
		\item \textcolor{bdf}{On-site Assistance}
			\begin{itemize_3pt}
			\item \textcolor{bdf}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textcolor{bdf}{experience, with a small nudge} (Kolb, 1984).
			\item Facilitated by local lay person
			\end{itemize_3pt}
			\vspace{0.05in}
%\bigskip
%			$\rightarrow$ Horse race between role models and business counseling.
		\end{itemize_3pt}

@@

\begin{frame}
\frametitle{Research Questions}
	\begin{itemize_3pt}
	%\item \textcolor{bdf}{Local characterization}
	%\vspace{0.05in}
	%	\begin{itemize_3pt}
	%	\item Which practices are associated with high profits?
	%	\item How do successful businesses implement them?
	%	\end{itemize_3pt}
	%\vspace{0.05in}
	\item \textcolor{bdf}{Adoption}
		\begin{itemize_3pt}
		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
		\item If so, ...
			\begin{itemize_3pt}
			\item Does the type of experiential involvement matter?
			\end{itemize_3pt}
		\end{itemize_3pt}
    \vspace{0.3in}
	\item \textcolor{bdf}{Impact}
		\begin{itemize_3pt}
		\item Does firm profitability increase?
		\item If so, what are the channels?
		\end{itemize_3pt}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Business in the Sample}

@@

\begin{frame}
\frametitle{Best-practices Handbook}

@@

\begin{frame}
\frametitle{Handbook Content}

@@

	\end{table}}}
\begin{itemize_3pt}
\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
\end{itemize_3pt}
\end{frame}
